---
title: Setup
author: "Roopa Krithivasan"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Steps: 

After a number of failed attempts, I decided that it works best to create your function first in a blank script, and save it with the name of the function. Save it somewhere you can find it later. 

So, I created, the hagfish function, which is this:

```
hagfish_function <- function(love=T){
  if (love == T){
    print("hagfish need love too")
  }
  else {print ("hagfish are weird")
  }
}
```

Use new project > new directory > new package to create a package. Make sure to tick "git"

it will by default create a "hello" function if you don't tell it to populate the package with an existing function. 


In a new script:

Set working directory
setwd("~/Dropbox/Clark/2017-FALL/R/assignment1/rka1h")
document()
?rka1h
setwd("~/Dropbox/Clark/2017-FALL/R/assignment1")
install.packages("rka1h")
?rka1h
install_github("rkrithivasan/rka1h")

library(devtools)
devtools::install_github("roopakrithi/rka1h")

devtools::install_github("roopakrithi/rka1h")
?hagfish_function
hagfish_function(love=T)

setwd("~/Dropbox/Clark/2017-FALL/R/assignment1/rka1h")
devtools::use_vignette("setup")















Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
